Planning with Hierarchical Temporal Memory for Deterministic Markov Decision Problem

### 2021-04-16 reports/v1_0/talk_eng/slides.tex
initial commit

\begin{frame}{Introduction and motivation}
	\begin{itemize}
		\item why we need a model
		\item why we draw inspirations from human memory models
	\end{itemize}
\end{frame}

@@

\begin{frame}{Agent's architecture}
	- figure
	- explain how it works on a high level	
\end{frame}

@@

\begin{frame}{Results. Experimental setup 1}
	- explain setup
	- figures
	- results	
\end{frame}

\begin{frame}{Results. Experimental setup 2}
	- explain setup
	- figures
	- results	
\end{frame}

>>>>

\begin{frame}{Model-based RL}
	\begin{itemize}
		\item learning the environment allows using planning methods
		\item can remedy sample inefficiency of model-free RL
		\item popular choice - Artificial Neural Networks
		\item we used more human-like memory model - Hierarchical Temporal Memory (HTM)
	\end{itemize}
\end{frame}

@@

\begin{frame}{Agent's architecture}
    \includegraphics[width=.65\linewidth]{agent_scheme}
	- explain how it works on a high level	
\end{frame}

@@

\begin{frame}{Experiments in fixed environments}
\begin{columns}
	\begin{column}{.55\textwidth}
	Setup:
	\begin{itemize}
		\item fixed handcrafted mazes
		\item reward position changes every 100 episodes
	\end{itemize}

	\vspace*{12pt}
	Conclusions:
	\begin{itemize}
		\item better than random policy in any situations
		\item learns and adapt faster than DQN
		\item optimal solution requires planning horizon to be large enough to reach the reward from the initial state
	\end{itemize}

	\end{column}

	\begin{column}{.45\textwidth}
	\begin{center}
		\includesvg[width=\linewidth]{multi_way_v0__steps}
		\includesvg[width=\linewidth]{multi_way_v2__steps}
	\end{center}
	\end{column}
\end{columns}	
\end{frame}

\begin{frame}{Experiments in changing environments}
\begin{columns}
	\begin{column}{.55\textwidth}
	Setup:
	\begin{itemize}
		\item randomly generated mazes
		\item maze periodically changes too
		\begin{itemize}
			\item up: every 200 episodes
			\item bottom: every 20 episodes
		\end{itemize}
	\end{itemize}

	\vspace*{12pt}
	Conclusions:
	\begin{itemize}
		\item learns and adapt faster than DQN
		\item more stable performance - less degradation spikes
		\item suboptimal solutions with faster adaptation win over potentially optimal solutions unable to adapt in time
	\end{itemize}

	\end{column}

	\begin{column}{.45\textwidth}
	\begin{center}
		\includesvg[width=\linewidth]{gridworld_5x5_100_2_8_1337__steps}
		\includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__steps}
	\end{center}
	\end{column}
\end{columns}
\end{frame}
